04_DESeq_sexes

### 2019-12-23 analysis/04_LDA.Rmd
new plot

>>>>

m <- plotfacetresults2(LDA.gon, alllevels, "hypothalamus", 20) + labs(x = NULL) + theme(axis.text.x = element_blank()) +
    theme(legend.position = "top")  +  guides(fill = guide_legend(nrow  = 1))
n <- plotfacetresults2(LDA.pit, alllevels, "pituitary", 17) + theme(strip.text = element_blank()) + labs(x = NULL) + theme(axis.text.x = element_blank())
o <- plotfacetresults2(LDA.gon, alllevels, "gonads", 15) +
  theme(strip.text = element_blank())  + labs(x = NULL) + theme(axis.text.x = element_text(angle = 45, hjust = 1))
